%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{deedy-resume} % a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection{}{Sophia N. Wassermann}{
\href{mailto:so@sowasser.com}{so@sowasser.com} | \href{https://sowasser.com}{sowasser.com} | \href{https://twitter.com/sowasser}{{\small \faTwitter} @sowasser} | Ireland: +353 83 482 7820 
}


%------------------------------------------------
% Education
%------------------------------------------------

\sectionspace
\section{Education} 

\runsubsection{P\MakeLowercase{h}D  C\MakeLowercase{andidate} Marine Science}
\location{\textbf{Ryan Institute, National University of Ireland Galway}}
\location{Irish Research Council Government of Ireland Postgraduate Scholar}
\location{Will Receive October 2020}
\location{Supervisor: Prof. Mark P. Johnson}
Modelling the shoaling behaviour of mackerel in the field to improve stock assessment
methods and indicate stock condition.

\sectionspace % Some whitespace after the section

%------------------------------------------------
\runsubsection{MS\MakeLowercase{c}  Biodiversity \& Conservation (Distinction)}
\location{\textbf{Trinity College Dublin}}
\location{Received December 2016}
Effects of climate change and bird predation on bivalve populations in Dublin Bay from 1985-2015. Supervisors: Prof. Stephen Waldren, Prof. James G. Wilson, Dr. Andrew Jackson

\sectionspace % Some whitespace after the section

%------------------------------------------------
\runsubsection{BA Environmental Studies}
\location{\textbf{Vassar College}}
\location{Received May 2013}

\sectionspace % Some whitespace after the section
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Research Experience
%------------------------------------------------

\section{Research Experience}

\runsubsection{Fulbright U.S. Student Program: H\'{a}sk\'{o}l\'{i} \'{I}slands \& MARICE}

\location{September 2014 - June 2015 | Reykjav\'{i}k, Iceland}
\location{Supervisors: Dr. Gu\dh r\'{u}n Marteinsd\'{o}ttir, Dr. Niall McGinty}
Impact of environmental factors on the vertical distribution of capelin (\textit{Mallotus villosus}) during their spawning migration.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{The School for Field Studies: Center for Marine Resource Studies}

\location{August 2013 - July 2014 | South Caicos, Turks and Caicos Islands}
\location{Supervisors: Dr. Heidi Hertler, Dr. Edward Hind-Ozan, Dr. Alex Tilley, Dr. Charlotte de Fontaubert}
\begin{tightitemize}
\item Distance sampling for detection probability of invasive lionfish (\textit{Pterois volitans}).
\item Survey of beach topography for change with rising sea levels and effects on sea turtle nesting.
\item Investigation into tourist opinions of attractions featuring captive cetaceans.
\item Survey of coral reef benthic cover.
\item Led research and recreational dives, organism ID sessions, and field work for undergraduate students studying abroad.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Dr. John Long's Lab - Vassar College Department of Biology}

\location{September 2012 - May 2013 | Poughkeepsie, New York}
\location{Supervisors: Dr. John Long, Dr. Marianne Porter}
Swimming kinematics and schooling behavior of cownose rays (\textit{Rhinoptera bonasus}).

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{The School for Field Studies: Center for Marine Resource Studies}

\location{October 2011 - December 2011 | South Caicos, Turks and Caicos Islands}
\location{Supervisor: Dr. Alli Candemlo}
Habitat use by size of lionfish and possible competition with Nassau grouper (\textit{Epinephelus striatus}). Research was incorporated into undergraduate thesis.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{New York State Department of Environmental Conservation}

\location{September 2009 - December 2009 | Staatsburg, New York}
Progression of zebra mussel (\textit{Dreissena polymorpha}) invasion in the Hudson River.

\sectionspace % Some whitespace after the section
\sectionspace


%------------------------------------------------
% Work Experience
%------------------------------------------------

\section{Work Experience}


\runsubsection{NUI Galway Marine Science}

\location{Tutor | September 2018 - Present}
Working with students in small groups and alone before major deadlines for their Marine Science coursework. Providing support for writing, presentation, and study skills.

\sectionspace

%-----------------------------------------------


%----------------------------------------------------------------------------------------
%	SECOND PAGE
%----------------------------------------------------------------------------------------

\newpage % Start a new page

%------------------------------------------------

\center{\textbf{Sophia N. Wassermann | \href{mailto:so@sowasser.com}{so@sowasser.com}}}
\sectionspace

%------------------------------------------------

\begin{flushleft}

%------------------------------------------------
% Cont. of Work Experience
%------------------------------------------------

\sectionspace
\sectionspace

\runsubsection{Martin Ryan Institute \& NUI Galway Zoology, Earth \& Ocean Science}

\location{Laboratory \& Field Demonstrating | March 2017 - Present}
Demonstrator (teaching assistant) for undergraduates in the classroom, lab, and field for:
\begin{tightitemize}
\item Field Skills in Marine Science
\item Marine Zoology
\item 1st year Biology
\item Geographic Information Systems and Biostatistics
\end{tightitemize}


\sectionspace

\runsubsection{Becoming a Data Scientist - D\MakeLowercase{ata}S\MakeLowercase{ci}G\MakeLowercase{uide}}

\location{Assistant | January 2017 - September 2019}
Content generation including blog posts and links to resources for entering the data science field.

\sectionspace

%------------------------------------------------

\runsubsection{Zoological Journal of the Linnean Society}

\location{Language Editing | June 2017 - November 2018}
Copy-editing with a focus on English language support.

\sectionspace

%------------------------------------------------

\runsubsection{NUI Galway Academic Writing Centre}

\location{Writing Tutor | October 2016 - May 2017 | Galway, Ireland}
\begin{tightitemize}
\item Conducted one-on-one writing consultations.
\item Led workshops on exam preparation and presentation skills.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Vassar College Writing Center}

\location{Writing Consultant | September 2010 - May 2013 | Poughkeepsie, NY}
Held consultations with students on essays and personal writing.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{National Centers for Coastal Ocean Science }

\location{Intern | May 2011 - August 2011 | Silver Spring, MD}
Worked with NCCOS scientists and communications team to develop easily-comprehended material for the website.

\sectionspace 
\sectionspace


%------------------------------------------------
% Publications
%------------------------------------------------

\section{Publications} 

\runsubsection{Papers}
\begin{tightitemize}
\item \textbf{Wassermann, S.N.}, E.J. Hind-Ozan \& J. Seaman. 
Reassessing public opinion of captive cetacean attractions with a photo elicitation survey. \textit{PeerJ} 2018.
\item Tilley, A., E. Carter, \textbf{S. Wassermann} \& J. Lopez Angarita. Enhancing management effectiveness of invasive lionfish using distance sampling and detection probability. \textit{Aquatic Conservation} 2015.
\end{tightitemize}

\sectionspace

\runsubsection{Presentations}
\begin{tightitemize}
\item \textbf{Wassermann, S.N.} Modelling collective behaviour to improve population estimates for pelagic fishes. Invited talk: Zoology, NUI Galway. 2019.
\item \textbf{Wassermann, S.N.} \& M.P. Johnson. Oh Behave! Building an individual-based model of shoaling behaviour to improve population estimates. ICES Annual Science Conference 2019. Gothenburg, Sweden. Poster.
\item \textbf{Wassermann, S.N.} Using collective behaviour for sustainable fishing. Invited talk: Department of Psychology, NUI Galway. 2019.
\item \textbf{Wassermann, S.N.} \& M.P. Johnson. It's wrong, but is it useful? Validating theoretical models of fish collective behaviour. 2nd Ecology and Evolution Ireland Conference 2019. Galway, Ireland. Poster.
\item \textbf{Wassermann, S.N.} \& M.P. Johnson. Modelling the shoaling behaviour of Atlantic mackerel to improve stock assessment methods. Ecology Across Borders 2017, Ghent, Belgium. Poster.
\item \textbf{Wassermann, S.N.} \& M.P. Johnson. Fish of a Feather: Modelling the shoaling behaviour of mackerel in the field to improve stock assessment methods. Marine Biological Association Postgraduate Conference 2017, Penryn, Cornwall. Oral Presentation.
\item \textbf{Wassermann, S.N.}, N. McGinty, A. \'{O}lafsd\'{o}ttir \& G. Marteinsd\'{o}ttir. The impact of environmental factors on capelin behaviour during the spawning migration. International Marine Conservation Congress 2016, St. John's, Newfoundland \& Labrador. Oral Presentation.
\item \textbf{Wassermann, S.} \& E. Hind. Tourist attitudes towards captive marine mammal attractions in the Turks and Caicos Islands. International Marine Conservation Congress 2014, Glasgow, Scotland. Poster.
\item Long, J.H., \textbf{S. Wassermann}, A. Siciliano, \& M.E. Porter. When fish school and when they don't: Test of a simple network model. The Society for Integrative \& Comparative Biology Annual Conference 2014, Austin, Texas. Poster.
\end{tightitemize}

\sectionspace


\end{flushleft}


%----------------------------------------------------------------------------------------
%	THIRD PAGE
%----------------------------------------------------------------------------------------

\newpage % Start a new page

%------------------------------------------------

\center{\textbf{Sophia N. Wassermann | \href{mailto:so@sowasser.com}{so@sowasser.com}}}
\sectionspace

%------------------------------------------------

\begin{flushleft}

\sectionspace

%------------------------------------------------
% Activities
%------------------------------------------------

\section{Leadership and Service} 

\runsubsection{Elected Positions}

\begin{tightitemize}
\item Student Representative to the Society for Conservation Biology (SCB) Marine Section Board \& the SCB Global Student Affairs Committee, 2017-2020. 
\item Assistant Editor (Engineering, Mathematics, and Science) of the Trinity Postgraduate Review 2016.
\item Vassar College Student Association residence president 2010-2011 \& 2012-2013.
\end{tightitemize}

\sectionspace

\runsubsection{Volunteer Work}
\begin{tightitemize}
\item Co-Chair of the 6th International Marine Conservation Congress, 2020, Kiel, Germany.
\item Deputy Co-Chair \& Student Activities Chair of the 5th International Marine Conservation Congress, 2018, Kuching, Malaysia.
\item SCB Awards Committee member, 2017-2020.
\end{tightitemize}

\sectionspace

%------------------------------------------------
% Certifications & Skills
%------------------------------------------------



\section{Awards \& Funding}
\sectionspace

\begin{tightitemize}
\item  \textbf{Irish Centre for High-End Computing (ICHEC)} - High Performance Computing (HPC) National Service Project, Class C
\item \textbf{Marine Institute Ireland} - Networking and Travel Grant for ICES Annual Science Conference, 2019
\item \textbf{Marine Institute Ireland} - National Research Vessels Ship-Time Grant-Aid (Principal Participant) for CV18012, 2018
\item \textbf{EuroMarine} - Young Scientist Fellowship Programme for Training, 2017
\item \textbf{Ryan Institute} - Travel Support Scheme, 2017
\item \textbf{Marine Biological Association} - Student Member Bursary, 2017
\item \textbf{Irish Research Council} - Government of Ireland Postgraduate Scholarship, 2017
\item \textbf{NUI Galway} - PhD International Merit Scholarship, 2017
\item \textbf{Fulbright U.S. Student Program (Iceland)}, 2014
\item \textbf{Sigma Xi} - Scientific Research Honor Society, undergraduate award, 2013
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Certifications & Skills
%------------------------------------------------

\section{Certifications \& Skills}
\sectionspace

\begin{tightitemize}
\item \textbf{Certifications:} \textbf{PADI} Open Water Scuba Instructor, Enriched Air/EANx, Deep Diver, Search \& Recovery, Emergency O2 Provider; \textbf{BSAC} O2 Administration, Boat Handling, Compressor Operation; \textbf{Emergency First Response} Instructor; Personal Survival Techniques (PST) STCW-95 %Subscript for O2??
\item \textbf{Software \& Coding:} Python, R, \LaTeX, NetLogo, HTML/CSS, Adobe Creative Suite, ArcGIS, ODV
\item \textbf{Hardware:} CTD/Sonde, hyperspectral radiometer, flow cytometer
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Research Cruises
%------------------------------------------------

\section{Seatime Experience}
\sectionspace

\begin{tightitemize}
\item \textbf{RV Celtic Explorer} - Western European Shelf Pelagic Acoustic Survey (CE19010). Biologist (Fish Lab). Celtic Sea \& Bay of Biscay. 13 June - 4 July 2019.
\item \textbf{RV Celtic Explorer} - Celtic Sea Herring Acoustic Survey (CE18016). Biologist (Fish Lab). Celtic Sea, 18-28 October 2018. 
\item \textbf{RV Celtic Voyager} - Distribution of Nephrops larvae and associated oceanographic conditions (CV18012). Scientist. Celtic Sea and Irish Sea, 3-16 April 2018.
\item \textbf{SSV Corwith Cramer} - Sea Education Association Summer Program. Gulf of Maine, 15-30 July 2007.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\end{flushleft}
%----------------------------------------------------------------------------------------

\end{document}